Under-approximation of reachability in multivalued asynchronous networks

### 2013-04-02 parts/def-ph.tex
compress

\pref{cr:2prio} allows to distinguish two kinds of actions:
\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
which would allow the play of an infinite sequence of prioritised actions in “zero time”.
\begin{criterion}[2 priorities]
\label{cr:2prio}
%\paragraph{2 priorities}
  In this paper, we only consider Process Hitting with $2$ classes of priorities:
  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
\end{criterion}
%
\begin{criterion}[Bounded termination]
\label{cr:bounded}
%\paragraph{Bounded termination}
  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
  %Cycles are still allowed in $\PH$ however.
  %Formally :
  $$\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N \enspace.$$
\end{criterion}

In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
%A well-formed component may stand for a real biological component (protein, light, nutriment…).
\begin{definition}[Well-formed component ($\components$)]
\label{def:component}
  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
  $$\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2 \enspace.$$
  We call $\components$ the set of well-formed components.
\end{definition}

\pref{def:chainsactions} defines chains of prioritised actions,
and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
%as prioritised actions are used to update non-biological components.
%this restriction will prevent incoherent states between cooperative sorts ().
\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
  \begin{align*}
  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
  \end{align*}
\end{definition}
\begin{criterion}[Cycle-freeness between prioritised actions]
\label{cr:cyclefreeness}
%\paragraph{Cycle-freeness between actions of priority $1$}
  There is no cycle in chains of actions:
  $$\forall a \in \PHs, \PHh(a, a) = \emptyset \enspace.$$
\end{criterion}

>>>>

\pref{cr:2prio} allows to distinguish two kinds of actions:
\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
which would allow the play of an infinite sequence of prioritised actions in “zero time”.
\begin{criterion}[2 classes of priorities]
\label{cr:2prio}
%\paragraph{2 priorities}
  In this paper, we only consider Process Hitting with $2$ classes of priorities:
  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
\end{criterion}
%
\begin{criterion}[Bounded termination]
\label{cr:bounded}
%\paragraph{Bounded termination}
  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
  %Cycles are still allowed in $\PH$ however.
  %Formally :
  $\exists N \in \sN, \forall \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
\end{criterion}

In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
%A well-formed component may stand for a real biological component (protein, light, nutriment…).
\begin{definition}[Well-formed component ($\components$)]
\label{def:component}
  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
  $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) = 2$.\\
  We call $\components$ the set of well-formed components.
\end{definition}

\pref{def:chainsactions} defines chains of prioritised actions,
and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
%as prioritised actions are used to update non-biological components.
%this restriction will prevent incoherent states between cooperative sorts ().
\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
  \begin{align*}
  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} \in (\PHh^{(1)})^{s+1} &\mid s \in \sN, \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
  \end{align*}
\end{definition}
\begin{criterion}[Cycle-freeness between prioritised actions]
\label{cr:cyclefreeness}
%\paragraph{Cycle-freeness between actions of priority $1$}
  There is no cycle in chains of actions:
  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
\end{criterion}
